Cannibalism among the supermassive black holes

### 2019-03-10 paper.tex
Mostly additions to Results section.

\subsection{Mergers, Ejections and Kicks}
Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes across all galaxy simulations as a function of guest black hole mass.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs}
\label{fig:meosmbh}
\end{center}
\end{figure}

>>>>

\subsection{Mergers, Ejections and Kicks}
Figure \ref{fig:meosmbh} shows the distribution of merged, ejected and orbiting black holes across all galaxy simulations as a function of guest black hole mass.  Given the log distribution of masses and using $10^7\, M_{\odot}$ as the approximate midpoint, one can see the general trend of larger mass BHs tending to merge with their respective host BH, with     the lower mass BHs continuing to wander at $z=0$.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0.}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/kicked_stats.png}
\caption{Histogram of kicked SMBHs at z=0.}
\label{fig:kicked_stats}
\end{center}
\end{figure}

As can be seen in Figure \ref{fig:kicked_stats}, the vast majority of larger SMBHs ($\gtrapprox\, 10^7\, M_{\odot}$) are not kicked to higher orbits nor ejected from their galaxies, which at least partly explains why most of the merged SMBHs are in the greater mass brackets.  In contrast, most of the SMBHs below $10^7\, M_{\odot}$ are kicked (with a few of them being ejected).  in our simulations, no black holes that are kicked to higher orbits ever merged with their central host SMBH.
